
\documentclass{beamer}
\usetheme{Madrid}
\title{The Undeniable Case for DamageBDD}
\author{Steven Joseph}
\date{\today}

\begin{document}

\frame{\titlepage}

\begin{frame}
\frametitle{What if your team could disagree more—and perform better?}
High-performing teams don’t fear conflict.\\
They welcome it—because they’ve built systems that turn friction into fuel.\\
That’s what DamageBDD delivers.
\end{frame}

\begin{frame}
\frametitle{DamageBDD is not just about tests}
It’s about creating a shared language between developers, PMs, and stakeholders.\\
Where disagreement leads to insight—not derailment.
\end{frame}

\begin{frame}
\frametitle{DamageBDD in Action}
\begin{itemize}
  \item Specs become executable
  \item Edge cases get verified
  \item Assumptions get challenged—safely
\end{itemize}
This isn’t fragile software.\\
It’s resilient systems shaped by truth.
\end{frame}

\begin{frame}
\frametitle{What DamageBDD Enables}
\begin{itemize}
  \item Explore the data together
  \item Take different approaches and test them
  \item Clarify assumptions through verification
\end{itemize}
Disagreement becomes an asset.
\end{frame}

\begin{frame}
\frametitle{In a world of uncertainty...}
DamageBDD makes correctness a team sport.\\
You don’t need agreement—just a truth machine that records intent, behavior, and outcome immutably.
\end{frame}

\begin{frame}
\frametitle{When something breaks...}
No blame. Just trace, learn, and level up.\\
DamageBDD turns errors into evolution.\\
That’s how trust scales. That’s how peace emerges.
\end{frame}

\begin{frame}
\frametitle{The Smartest Teams Choose DamageBDD}
Because they want:
\begin{itemize}
  \item Resilience over fragility
  \item Clarity over confusion
  \item Alignment over assumption
\end{itemize}
DamageBDD is how top performers stay on top.
\end{frame}

\end{document}
